%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[resmargin]{res}
% \usepackage[margin=1in]{geometry}
    % \topmargin=-0.25in
	\addtolength{\oddsidemargin}{-.475in}
	\addtolength{\evensidemargin}{-.475in}
	\addtolength{\textwidth}{0.95in}
	
% Default font is the helvetica postscript font
\usepackage{helvet}
\usepackage{hyperref}
% Increase text height
\textheight=700pt

%Github
\usepackage{fontawesome5}
\usepackage{hyperref}

\begin{document}


%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{PIYUSH MALAV}



\address{Final Year Dual Degree Student\\ BTech - Electronics and Communication Engineering\\MTech - CSE Artificial Intelligence \\ GBU, Greater Noida,\\ UP, 201312}
\address{ E-Mail: piyushmalav85@gmail.com \\ Mob : +91 8955558388\\ GFG Profile: \href{https://auth.geeksforgeeks.org/user/piyushmalav/}{LINK}\\ Hackerrank Profile: \href{https://www.hackerrank.com/piyushmalav85?hr_r=1}{LINK}}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}

%----------------------------------------------------------------------------------------

\begin{resume}
\section{CAREER INTERESTS}
{Full Stack Development, Web Engineering, Machine Learning}

\section{ACADEMICS}
    \textbf{Gautam Buddha University, Greater Noida, Uttar Pradesh } \\
   B.Tech in Electronics and Communication Engineering, \textbf{8.22} (Completed) \hfill 2017 - Current \\
   M.Tech (Dual Degree) in CSE Artificial Intelligence (Ongoing)
   %\\
   
   \textbf{Sumit Bal Sr Sec School, Kota, Rajasthan}\\
   Rajasthan Senior Secondary Examination, Class 12th, \textbf{87\%} \hfill 2017
   
   \textbf{Ideal Public Sr Sec School, Keshavraipatan, Rajasthan}\\
   Rajasthan Secondary Examination, Class 10th, \textbf{86.83\%} \hfill 2014
 
  
 
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTIONs
%----------------------------------------------------------------------------------------

\section{ACHIEVEMENT}
 \textbf{Letter for Appreciation from GBU Vice Chancellor}
 \\ Received a letter for appreciation from GBU Vice Chancellor for acquiring \textbf{first rank in academic year 2018-2019} in BT-MT ECE program. \textbf{Awarded INR 20,000} for the achievement.

 \textbf{Consistent Academic Excellence}
 \\ Shown consistent academic excellence by securing \textbf{4th rank in first year}, \textbf{1st rank in second year}, and \textbf{2nd rank in third year} of BT-MT ECE program.

\section{MTECH\\ THESIS}

\textbf{Siamese Signature Verification Webapp (ongoing)} {\sl  \hfill}
\\{\sl \textbf{Metnor}: \href{https://sites.google.com/view/neetasingh112}{Dr. Neeta Singh}, Assistant professor, Gautam Buddha University, Greater Noida}
\\{\sl \textbf{Technologies}: Java8, MVC service repository pattern, Maven, Spring, Hibernate, ReactJS}
\\ A Resnet50 based siamese network implementation for sign recognition. A \textbf{Java Spring application} is being implemented to serve Tensorflow model with \textbf{React frontend}. The webapp incorporates enrollment and verification module with user data being persisted with \textbf{in-memory H2 database}.

\section{ONLINE\\ INTERNSHIP}

\textbf{Banking System WebApp
\href{https://www.youtube.com/watch?v=uO6ZealjeIA}{\faIcon{youtube}} \href{https://github.com/malavp1998/bank-management-service}{\faGitSquare} \href{https://github.com/malavp1998/bank-management-web}{\faGitSquare}} {\sl  \hfill Feb'2021 - Mar'2021}
\\{\sl \textbf{Association}: \href{https://www.thesparksfoundationsingapore.org/join-us/internship-positions/}{Graduate Rotational Internship Program (GRIP)}, The Sparks Foundation}
\\Implemented a Basic Banking System with Spring framework (Backend) and ReactJS (Frontend) which uses MySQL database to store and maintain the user data.
Provide functionality to add customers, view customers, transferring money from one customer to another customer.

\section{PROJECTS}

\textbf{Car Parking Reservation System \href{https://github.com/malavp1998/parking-lot}{\faGitSquare}
}{\sl\hfill}
\\ Implemented an car parking system using \textbf{Java OOPS} which provide functionality of making car entry using registration plate, finding an empty slot, calculating parking charges, etc. 

\textbf{Students Record Management System \href{https://github.com/malavp1998/springboot-with-mongoDB}{\faGitSquare} \href{https://github.com/malavp1998/spring-boot-SqliteDB}{\faGitSquare}} {\sl  \hfill}
\\{\sl \textbf{Technologies}: Java, OOPS, SQL}
\\ Implement student record management system using \textbf{object oriented paradigm} in \textbf{Java}, which uses \textbf{SQLite SQL database} management system to maintain and store student data. Provided capabilities to create, display, modify, and delete student marks record. 

\textbf{E-Commerce Application} {\sl  \hfill}
\\{\sl \textbf{Technologies}: Java8, Spring, Hibernate, MySQL, JQuery}
\\ Course project to implement online bookstore with modern \textbf{Java Full Stack} technologies. The website architecture is divided in two parts: Bookstore and AdminPortal. The backend side make use of \textbf{Spring Boot}, Spring Security with data persistence in MySQL. The frontend code include normal HTML, CSS, JavaScript, Thymeleaf etc.   

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{RELEVANT\\ COURSES}
Complete E-Commerce Course - Java Spring Hibernate and MySQL, Go Java Full Stack with Spring Boot and React, Data Structures and Algorithms, The Ultimate MySQL Bootcamp: Go from SQL Beginner to Expert, The Web Developer Bootcamp, C++: Programming from Beginner to Beyond,

\section{TECHNICAL\\SKILLS}

\textbf{Languages}: Java (Spring, Hibernate JPA, Maven, Lombok), C, C++, Python (intermediate) \\
\textbf{Web Dev}: ReactJS, JavaScript, HTML, CSS            \qquad \textbf{Databases}: MySQL, SQLite, MongoDB

% \section{EXTRA-CURRICULAR ACTIVITIES}

%  \textbf{Member of Football Team}
%  \\ Playing as an important right back in college football team. Awarded Silver medal in inter college tournament.

%Smart Grid: Make another section for participation.


\end{resume}
\end{document}